\cvsection{Experience}

\begin{cventries}
  \cventry
    {Researcher} % Job title
    {Montana State University} % Organization
    {Bozeman, MT} % Location
    {July 2021 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesign backend computation for algebraic structure decreasing computation speed more than 100 fold through just-in-time compiling and multithreading.}
        \item {Build and maintain research compository and documentation in accessible fashion.}
        \item {Research parallels between Farey Diagram and two-bridge knots and links.}
        \item {Efficently design and computer Q-Algebra to specificed denominator for insight into representation as a Hausdorff set.}
        \item {Present at NCUR, PiMuc, and Montana State Math Seminars on research findings}
      \end{cvitems}
    }
  \cventry
      {CS Intern}
      {Foundant Technologies}
      {Bozeman, MT}
      {May 2021 - PRESENT}
      {
        \begin{cvitems}
          \item {Design and implement CSS/HTML frontend and JS components for custom designed to visuals to client specification.}
          \item {Improve UI design and documentation process allowing more junior or non-technical staff options to pursue independent builds without engineering support.}
          \item {Helped reduce one-touch metric for engineering focused issues from 3 days to less than 5 hours.}
          \item {Work with engineering and product teams to effectively manage issues and performance in AWS instances via Kibana and Elastic dashboards.}
          \item {Utilized an agile framework in Jira to effectively manage and track user stories for proper time management.}
          \item {Take charge on low-level tickets with over 1250 issues approved and completed.}
        \end{cvitems}  
      }
  \cventry
        {Junior Underwriter}
        {Trade Risk Guaranty}
        {Bozeman, MT}
        {January 2019 - May 2021}
        {
          \begin{cvitems}
            \item {Advanced cash-flow analysis to model client inefficiencies and potentially credit loss.}
            \item {Work directely with clients to effectively manage bond sufficiency and potential legal issues due to Anti-Dumping/Countervailing entries.}
            \item {Coordinated collection and placement of collateral for bond underwriting.}
            \item {Work directly with surety to manage and approve underwriting decisions.}
          \end{cvitems}
        } 
\end{cventries}
